Katana: A Userland Toolchain-Oriented Hotpatching System

### 2010-06-23 doc/katana.tex
more slight license massaging

% Created 2010-06-20 Sun 23:06
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{soul}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{graphicx}

\title{Katana: A Userland Toolchain-Oriented Hotpatching System}
\author{James Oakley}
\date{20 June 2010}

@@

  Katana is under development at Dartmouth College and Copyright 2010
  Dartmouth College. It may be distributed under the terms of the GNU
  General Public License with attribution to Dartmouth College as
  specified in the file COPYING distributed with Katana. This document
  is Copyright 2010 Dartmouth College and may be distributed under the
  terms of the GNU Free Documentation License

>>>>

% Created 2010-06-22 Tue 19:27
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{soul}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{graphicx}

\title{Katana: A Userland Toolchain-Oriented Hotpatching System}
\author{James Oakley}
\date{22 June 2010}

@@

  Katana is under development at Dartmouth College and Copyright 2010
  Dartmouth College. It may be distributed under the terms of the GNU
  General Public License with attribution to Dartmouth College as
  specified in the file COPYING distributed with Katana. This document
  is Copyright 2010 Dartmouth College and may be distributed under the
  terms of the GNU Free Documentation License as found in the file FDL
  which should have been distributed with this documentation. If it
  was not, it may be found at \href{http://www.gnu.org/licenses/fdl.txt}{http://www.gnu.org/licenses/fdl.txt}.
